---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE,
  message = FALSE
)
```

# chicagoDA

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/chicagoDA)](https://CRAN.R-project.org/package=chicagoDA)
<!-- badges: end -->

The goal of chicagoDA is to facilitate access to the Cook County State Attorney's Office data published recently by the Cook County Government. The package is named `chicagoDA` as Chicago is the most famous city within Cook County and thus will be more recognizable.

## Installation

You can install the GitHub version of chicagoDA from [GitHub](https://github.com/ian-flores/chicagoDA) with:

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github('ian-flores/chicagoDA')
```

## Datasets

```{r libraries}
library(chicagoDA)
library(tidyverse)
```

### Intake

```{r intake-glimpse}
glimpse(intake)
```

```{r intake-docs, eval=FALSE}
?intake
```
