---
title: "Getting Started with the Data"
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE
)
```

```{r setup}
library(chicagoDA)
library(tidyverse)
library(lubridate)
```

## Datasets

There are 4 datasets included in the package. All of them are filtered for cases **received** by the State Attorney's Office during 2019. If you wish to extract cases from before or after 2019 you'll need to use the `get_all_data()` function. This is given size constraints for packages.

### **Intake**
  
- *Observational Unit*: Case
- *Rows*: 36,190
- *Variables*: 17
- *Description*: Arrests brought in for review by the SAO
  
```{r}
intake %>%
  group_by(date = ymd(received_date)) %>%
  count() %>%
  ggplot(aes(x = date, y = n)) +
    geom_point() +
    geom_smooth() +
    labs(x = 'Date',
         y = 'Received Cases',
         title = 'Is the number of received cases constant through out the year?')
```

### **Initiation**

- *Obersvational Unit*: Charge
- *Rows*: 73,029
- *Variables*: 27
- *Description*: Arrests that turned into cases

```{r}
library(forcats)

initiation %>%
  filter(law_enforcement_agency == 'CHICAGO PD',
         race != '') %>%
  add_count(updated_offense_category, race) %>%
  select(updated_offense_category, race, n) %>%
  unique() %>%
  group_by(updated_offense_category) %>%
  mutate(crime_count = sum(n)) %>%
  ungroup() %>%
  group_by(race) %>%
  top_n(20) %>%
  ungroup() %>%
  ggplot(aes(x = fct_reorder(updated_offense_category, crime_count, .desc = F), 
             y = log(n),
             colour = race, 
             fill = race)) +
    geom_bar(stat = 'identity') +
    coord_flip() +
    labs(y = 'Log of the number of charges initiated by arrests made by Chicago PD',
         x = 'Type of Charge',
         title = 'In what cases does Chicago PD focuses?',
         subtitle = 'Showing top 20 charges brought up, per race')
```

### **Dispositions**

- *Observational Unit*: Charge
- *Rows*: 20,234
- *Variables*: 31
- *Description*: How the charges turned out (guilty, not guilty, dismissed, etc)

```{r}
dispositions %>%
  group_by(race, charge_disposition) %>%
  count() %>%
  ungroup() %>%
  group_by(charge_disposition) %>%
  mutate(charge_n = sum(n)) %>%
  filter(race != '') %>%
  ggplot(aes(x = fct_reorder(charge_disposition, charge_n), y = log(n), fill = race)) +
    geom_bar(stat = 'identity') +
    coord_flip() +
    labs(y = 'Log of the number of dispositions',
         x = 'Disposition Status',
         title = 'Are the differences by race in the disposition of charges?',
         subtitle = 'Data for all Cook County')
```

### **Sentencing**
  
- *Observational Unit*: Charge
- *Rows*: 4,329
- *Variables*: 39
- *Description*: Sentence imposed to a charge

```{r}
sentencing %>%
  filter(commitment_type == 'Illinois Department of Corrections',
         race != '', race != 'Unknown') %>%
  ggplot(aes(x = age_at_incident, y = as.numeric(commitment_term))) +
    geom_point() +
    geom_smooth(method = 'lm') +
    labs(x = 'Age at Incident',
         y = 'Sentence (Years)',
         title = 'Do younger prisioners get harsher sentences?') +
    facet_wrap(~ race)
```
